---
title: "Task 19"
subtitle: "My Stocks Better than Yours"
date: 6/23/2020
output: 
  html_document:
    keep_md: true
---

```{r include=FALSE}
library(tidyquant)
library(quantmod)
library(lubridate)
library(tidyverse)
library(plotly)
library(ggplot2)
library(readr)
library(dplyr)
library(foreign)
library(haven)
```

## Background

**Three stocks for my friend : Delta Airlines (DAL),Netflix(NFLX),Snapchat(SNAP). My three stocks: Twitter(TWTR),Walmart(WMT),Zoom Communications (ZM)**

## Perfomane Analysis

```{r}
w<-tq_get("ZM",get= "stock.prices",from="2019-10-01",to="2020-06-20")
y<-tq_get("NFLX",get="stock.prices",from="2019-10-01",to="2020-06-20")
s<-tq_get("SNAP",get="stock.prices",from="2019-10-01",to="2020-06-20")
tw<-tq_get("TWTR",get="stock.prices",from="2019-10-01",to="2020-06-20")
wm<-tq_get("WMT",get="stock.prices",from="2019-10-01",to="2020-06-20")
d<-tq_get("DAL",get="stock.prices",from="2019-10-01",to="2020-06-20")
t <- bind_rows(w,y,s,tw,wm,d)
t
k<-t %>% group_by(symbol) %>% tq_transmute(adjusted,mutate_fun=dailyReturn,col_rename="Ra")
k$Ra<- k$Ra*1000
k1 <- mutate(k,Day=wday(date,label=TRUE),date=date(date),Month=month(date,label=TRUE))
k1
```

```{r,fig.width=12}
p<-ggplot(k1,aes(Day,Ra,col=symbol))+theme_tq()+scale_color_tq()+geom_boxplot(aes(Day))+facet_wrap(~symbol)+labs(x="Day",y="Daily Returns",color="STOCKS",title="Stocks Performance on Daily Basis (October 2019- June 2020)")
ggplotly(p,tooltip=c("Day","Ra","symbol"))
```
```{r}
k2 <- k1 %>% group_by(symbol) %>% summarise(sum=sum(Ra))
o<-ggplot(k2,aes(symbol,sum,col=symbol,size=sum))+geom_point()+ggtitle("Investment Growth per Stock")
ggplotly(o, tooltip="sum")

```

## Summary

**My friend picked three stocks: Delta Airlines(DAL),NetFlix(NFLX), and SnapChat(SNAP).
I picked three stocks : Twitter(TWTR),Walmart(WM),and Zoom Communications (ZM)
Over the past 8 months, Zoom communications has had the greatest returns. Snapchat and Netflix did better than Walmart. Twitter and Delta Airlines were the worst stocks to invest in over the past 8 months. The $1000 didn't generate any positive returns. Investing in Delta Airlines and Twitter resulted in a huge loss.**