---
title: "Task 21"
author: "Exode"
date: "6/28/2020"
output: 
  html_document:
    keep_md: true
---

```{r include=FALSE}
library(ggplot2)
library(USAboundaries)
library(sf)
library(tidyverse)
library(maps)
library(ggrepel)
library(pander)
library(DT)
library(dplyr)
library(Lahman)
library(tidyr)
library(ggspatial)
library(plotly)
library(png)
```

```{r}
citation("USAboundaries")
```

```{r}

states_2020 <- us_cities()
y<-states_2020 %>% extract(geometry, c("Latitude", "Longitude"), "\\(([^,]+), ([^)]+)\\)")
y1 <- st_as_sf(y)
states_20 <- us_states()
states_2<-subset(states_20,state_name!="Alaska"&state_name!="Hawaii"&state_name!= "Puerto Rico")
st <- us_counties(state="idaho")


t <-as.data.frame(states_2020 %>%
group_by(state_name) %>% top_n(3,population))
t2<-st_as_sf(t)
t3 <- subset(t2,state_name!="Alaska"&state_name!="Hawaii"&state_name!= "Puerto Rico")

t3$population<-t3$population/1000
t4 <-as.data.frame(t3 %>%
group_by(state_name) %>% top_n(1,population))
t5<-st_as_sf(t4)


```
```{r,fig.width=100,fig.height=90}
m <- ggplot()+geom_sf(data=states_2,fill=NA,size=5)+geom_sf(data=t3,aes(color=city),show.legend = FALSE)+geom_sf(data=st,fill=NA)+geom_point(data=t3,aes(size=population,geometry=geometry),stat="sf_coordinates")+theme_bw(base_size = 120)+scale_size_continuous(range = c(30, 50))+labs(size="Population (1000)",title="U.S Map with the Three Biggest Cities in Each State")+theme(axis.title.x = element_blank(),
          axis.title.y = element_blank())+  geom_sf_label(data=t5,aes(label = city), size=22,color="blue",label.padding = unit(10, "mm"),fontface="bold")
m


ggsave('~/saved_image.png', width = 40, height = 20, dpi = 200)